Partial rank data with the \pkg{hyper2} package: likelihood functions for generalized Bradley-Terry models

### 2019-05-06 inst/collusion_chess_draws.Rnw
work

<<>>=
jj <- read.table("stockholm1962.txt",header=FALSE)
results <- as.matrix(jj[,-(1:2)])
players <- as.character(jj$V1)
nationality <- as.character(jj$V2)
rownames(results) <- players
colnames(results) <- substr(players,1,1)
results
@

(this taken from Wikipedia
\url{https://en.wikipedia.org/wiki/World_Chess_Championship_1963}).
In this dataset, "0" means a loss, "1" a draw and "2" a win.  Thus
Fisher (row 1) beat Korchnoi (column 4).  As a consistency check we
verify that the results table is antisymmetric:

<<>>=

all(t(results) == 2-results)
which(results != 2-t(results),arr.ind=TRUE)
@

Thus Barcza vs Portisch is problematic.  Glossing over this

@@

\begin{table}
\centering
\begin{tabular}{l|ccccc}
& \rotatebox{-90}{Fisher} 
&\rotatebox{-90}{Geller} 
&\rotatebox{-90}{Petrosian} 
&\rotatebox{-90}{Korchnoi} 
&\rotatebox{-90}{Filip} 
\\ \hline
  Fisher       & - & \half&\half& 1&\half\\
Geller &\half&-&\half&\half&\half\\
Petrosian &\half&\half&-&\half&\half\\
Korchnoi &0&\half&\half&-&1\\
Filip &\half&\half&\half&0\\
\end{tabular}
\end{table}

>>>>

@@

\begin{table}
\centering
\begin{tabular}{l|cccccc}
& \rotatebox{-90}{Fisher} 
&\rotatebox{-90}{Geller} 
&\rotatebox{-90}{Petrosian\ }
&\rotatebox{-90}{Korchnoi} 
&\rotatebox{-90}{Filip}
& $\cdots$
\\ \hline
  Fisher   (USA)    & - & \half&\half& 1&\half&\\
Geller (USSR) &\half&-&\half&\half&\half&\\
Petrosian (USSR) &\half&\half&-&\half&\half&\\
Korchnoi (USSR) &0&\half&\half&-&1&\\
Filip (TCH)&\half&\half&\half&0&\\
$\vdots$&&&&&\\

\end{tabular}
\end{table}
